DOpElib - Deal Optimization Environment

### 2012-08-20 Examples/Documentation/introduction.tex
Corrected Docu for MacOSX

  If \texttt{which g++} only returns one g++ compiler, then probably you need to
  set an appropriate symlink.

  For example on Mac OSX you will find only one g++ compiler \texttt{/usr/bin/g++}
  which is in fact a symlink to \texttt{/usr/bin/g++-4.2}. Thus to change, the 
  desired behavior you should add a new link named \texttt{g++} in a directory 
  in front of \texttt{/usr/bin} or replace the symlink in \texttt{/usr/bin}
  with a link to the newer compiler which may be for instance located (macports 
  g++ 4.5 on OSX Lion) in \texttt{/opt/local/bin/g++-mp-4.5}. Make shure that 
  you add additional appropriate links to \texttt{gcc, cc, }and \texttt{c++}.

>>>>

  If \texttt{which g++} only returns one g++ compiler, then probably you need to
  set an appropriate symlink. Or more robust, you can configure \texttt{dealii}
  to use the compiler you intend by configuring deal with the right compiler. To
  do so adjust  the \texttt{CC} and \texttt{CXX} environment variable appropriately
  before configuring \texttt{dealii}

  For example on Mac OSX you will find only one g++ compiler \texttt{/usr/bin/g++}
  which is in fact a symlink to \texttt{/usr/bin/g++-4.2}. 
  So that you need to insall a newer compiler this may then be found ,e.g., using macports 
  g++ 4.5 on OSX Lion, in \texttt{/opt/local/bin/g++-mp-4.5}.
